\TheTitle

### 2015-08-14 linvis.tex
Introduction: Re-working intro and related works

Maintainers of older version of the Linux kernel must sift through thousands of
commits with tools that are unable to filter and effectively visualize projects
that are of the scale of the kernel. Tools like gitk provide users with the
full view of the DAG, showing all merges and commits. For smaller projects,
this information is useful to show the relation between various branches.
With larger, modular projects like the Linux Kernel, the DAG becomes a tangled
mess (\ref{fig:gitk}). Github provides a DAG view for most projects, but is
unable to display the DAG of projects as large as the Linux Kernel.

@@

Another issue with performing searches is that git log, gitk, and other tools
only store the authored date of a commit. A commit may be merged at any time,
regardless of when the commit was authored. Because of this, performing
date-range queries does not provide meaningful results. Performing a date-range
query using other tools over the span of a release will contain results that
are for previous versions of the kernel, and may not contain all of the results
for that kernel if patches were merged after the release date.

German et al. recorded the metadata of every commit and merge in the Linux git
repository from 2012 to 2015, including data that is not stored by git. We are
able to use this information to generate sets of trees instead of a DAG. The
root node of each tree is the top-level merge performed by Linus, which merges
a given commit into the kernel.

In this paper, we present the design decisions behind a web-based tool,
demonstrating the advantages of our tree model over the use of a DAG. Our tool
provides information about the location of a given commit in the respective
merge tree, the files edited, the modules edited, and the commit message in a
given commit or merge. The tool allows users to apply various filters,
including the release, a keyword or phrase from the log preview, the name of
the author, or the commit id. The user can request all the top-level merges
containing a commit or merge that matches the query, or all commits and merges
that match the query.

Our model of the tool provides many advantages other tools. Breaking the data
by merge tree removes the commits and merges to other components of the kernel
from the visualization, providing a clearer picture of what is happening in a
given merge.

No top-level merges are merged to an earlier version of the kernel after the
release date. Because of our tree construction, we are able to use these
top-level merges to find all merges effecting a version of the kernel,
regardless of when they were authored and merged. This provides us with
mechanisms for performing date-range queries that are able to provide
meaningful information.

@@

\subsection{Gitk}
Gitk, Gitg, and other similar git repository visualizing tools use the DAG as
the central organization. For smaller projects, this model is sufficient for
providing meaningful information, but in larger projects like the Linux kernel,
the branches become too tangled and too deep to derive any meaning from the
DAG. The DAG model allows users to go to the next commit in the chain, go to
the previous commit in the chain, or jump to the parent merge. This suggest
that gitk and similar tools are designed for users working with a bottom-to-top
approach. With this model, it is difficult for users to see what other commits
are involved with a given merge. Gitk only provides file information on
commits, as it is unable to quickly find all files edited by a merge. It is up
to the user to remember what files were edited in each of the commits involved
in a given merge. For some of the large merges in the Kernel, this is an
impossible task. \evantodo{Find a large one and report how many files are
there} Other DAG visualization systems, like the GitHub viewer, are unable to
provide a visualization for projects that are as large as the
kernel.\evantodo{Show picture of github failing}

@@

% \begin{figure}[h!]
% 	\centering
% 	\includegraphics[width=0.47\textwidth]{figures/empty.png}
% 	\caption{}
% 	\label{}
% \end{figure}

\subsection{Treemap visualizer}
University of Maryland presented a treemap design for displaying all the files
in a given release. Treemaps are good for displaying the topology of shallow,
wide trees, making it a good candidate for displaying file systems. Treemaps
are limited in what information can be displayed. The information within the
treemap does not provide clear insight on what changes were made to the files
in the given release. The treemap visualization only provides information on
where the file is located within the filesystem\ref{fig:treemap}. File systems
and the merge tree of the kernel share many similarities, in both cases, the
representative trees are wide and shallow, suggesting that a treemap could
potentially work to visualize the commit and merge structure of the kernel.

@@

We use a tree.

@@

Our primary focus was looking for a way to remove as much information as
possible to narrow the results that we wanted to return. Right now, the largest
set of data that a search could return is the entire set of commits that
pertain to a given release. While this set is massive, it pales in comparison
to every commit and merge generated for all versions of the kernel. From there,
the design is centered around the merge tree. These are all of the commits and
merges that eventually are merged by a top-level merge into the kernel. The
design centers around a vine-shape. The top-level merges form a linked list,
each node being a logical section within the kernel. These sections are defined
by Linus. Within each of these top-level merges is a tree of merges and
commits. The merges form the inner-nodes, and the commits form the leaf-nodes.

@@

% Database
We split the data presented among 5 tables; commits, filesmod, logs,
pathtomerge, and releases. The commits table stores the metadata about a given
commit or merge. This includes the author, the authored date, the committer,
commit date, and the file-level diff. The filesmod table stores the information
about the files modified in a commit. We have the commit id, or cid, of the
commit, the filename, the number of lines added and the number of lines removed
from the file. There may be multiple files within a given commit, and there may
be multiple commits editing the same file, the database uses an index as the
primary key, though the primary key could be the cid, filename pair.

% Tables
commits
filesmod
logs
pathtomerge
releases

>>>>

Maintainers of older version of the Linux kernel must sift through thousands of
commits with tools that are unable to filter and effectively visualize projects
that are of the scale of the kernel. Tools like Gitk provide users with the
full view of the DAG, showing all merges and commits. For smaller projects,
this information is useful for showing the relation between various branches.
With large modular projects, like the Linux Kernel, the DAG becomes a tangled
mess (\ref{fig:gitk}) of commits, merges, and the links between them, making it
difficult to derive an explanation of the changes.  Github provides a DAG view
for most projects, but is unable to display the DAG of projects as large as the
Linux Kernel.

@@

Git log, Gitk, and other similar tools only store the authored date of a
commit. A commit may be merged into the project at any time, regardless of when
the commit was authored. Because of this, performing date-range queries does
not provide meaningful results. Performing a date-range query using other tools
over the span of a release will contain results that are for previous versions
of the kernel, and may not contain all of the results for that kernel if
patches were merged after the release date.

German et al. recorded the metadata of every commit and merge in the Linux git
repository from 2012 to 2015, including data that is not stored by git. We are
able to use this information to generate sets of trees instead of a DAG. The
root of each tree is the top-level merge performed by Linus, which merges a
given commit into the kernel.

In this paper, we present the design decisions behind a web-based tool built
around a tree-based model instead of the DAG. We demonstrate the advantages of
this model over the use of the DAG. Our tool provides information about the
location of a given commit in the respective merge tree, the files edited, the
modules edited, and the commit message in a given commit or merge. The tool
allows users to apply various filters, including the release, a keyword or
phrase from the log preview, the name of the author, or the commit id. The user
can request all the top-level merges containing a commit or merge that matches
the query, or all commits and merges that match the query.

Our core model provides many advantages to other tools. Breaking the data by
merge tree removes the commits and merges of other components of the kernel
from the visualization, providing a clearer picture of what is happening in a
given merge. This model provides additional support to edited file information.

All top-level merges to a given version of the kernel are merged between the
start and release date. Our tree construction allows us to use the top-level
merges to find all merges and commits that have an effect on a given version of
the kernel. The model allows us to better provide mechanisms for performing
date-range queries, providing access to all commits that have an effect on a
given release, even if the commit comes before the start date, or the release
date.

@@

\subsection{Gitk}
Gitk, Gitg, and other similar git repository visualizing tools use the DAG as
the central organization. For smaller projects, this model is sufficient for
providing meaningful information, but in larger projects like the Linux kernel,
the branches become too tangled and too deep to derive any meaning from the
DAG. The DAG model allows users to go to the next commit in the chain, go to
the previous commit in the chain, or jump to the parent merge. This suggest
that Gitk and similar tools are designed for users working with a bottom-to-top
approach. With this model, it is difficult for users to see what other commits
are involved with a given merge. Gitk only provides file information on
commits, as it is unable to quickly find all files edited by a merge. It is up
to the user to remember what files were edited in each of the commits involved
in a given merge. In some of the larger merges, some containing over 1500
edited files, this task become nearly impossible.
% cid: 73287a43cc79ca06629a88d1a199cd283f42456a, 1800 commits, 1500 files
Other DAG visualization systems, like the GitHub viewer (\ref{fig:gitfail}),
are unable to provide a visualization for projects that are as large as the
kernel.

\begin{figure}[h!]
	\centering
	\includegraphics[width=0.45\textwidth]{figures/github_viewer.png}
	\caption{Github Failure Message}
	\label{fig:gitfail}
\end{figure}

@@

\subsection{Treemap visualizer}
University of Maryland presented a treemap design (\ref{fig:treemap}) for
displaying all the file structure of a given version. Treemaps are good for
displaying the topology of shallow, wide trees, making it a good candidate for
displaying file systems. Treemaps are limited in what information can be
displayed. The information within the treemap does not provide clear insight on
what changes were made to the files in the given release. The treemap
visualization only provides information on where the file is located within the
filesystem. File systems and the merge tree of the kernel share many
similarities, in both cases, the representative trees are wide and shallow,
suggesting that a treemap could potentially work to visualize the commit and
merge structure of the kernel.

@@

@@

The goal is to build a system that allows users to easily navigate and
understand the changes within the kernel. To do this, the user must have the
ability to perform searches

The goal was to build a system that would allow users to easily navigate the
commit information of

Our primary focus was looking for a way to remove as much unnecessary
information as possible narrow the results.

information as
possible to narrow the results that we wanted to return. Right now, the largest
set of data that a search could return is the entire set of commits that
pertain to a given release. While this set is massive, it pales in comparison
to every commit and merge generated for all versions of the kernel. From there,
the design is centered around the merge tree. These are all of the commits and
merges that eventually are merged by a top-level merge into the kernel. The
design centers around a vine-shape. The top-level merges form a linked list,
each node being a logical section within the kernel. These sections are defined
by Linus. Within each of these top-level merges is a tree of merges and
commits. The merges form the inner-nodes, and the commits form the leaf-nodes.

@@

% Database
We split the data presented among five tables; commits, filesmod, logs,
pathtomerge, and releases. The commits table stores the metadata about a given
commit or merge. This includes the author, the authored date, the committer,
commit date, and the file-level diff. The filesmod table stores the information
about the files modified in a commit. We have the commit id, or cid, of the
commit, the filename, the number of lines added and the number of lines removed
from the file. There may be multiple files within a given commit, and there may
be multiple commits editing the same file, the database uses an index as the
primary key, though the primary key could be the cid, filename pair.

% Tables
% commits
% filesmod
% logs
% pathtomerge
% releases

%
